Gravitational wave sources in our Galactic backyard: LISA predictions for BH and NS binaries

### 2021-06-15 paper/tex/sections/discussion.tex
progress on distinguishing

\subsubsection{Distinguishing from WDWD population}
\subsubsection{Separating BHBHs, BHNSs and NSNSs}

\subsection{Matching LISA detections to pulsars with SKA}\label{sec:pulsar_matching}
Since the vast majority of the LISA detectable population of DCOs will not merge for many years, the main form of electromagnetic counterpart for the this population is pulsars. Therefore, for this section we focus only on BHNSs and NSNSs since no BHBH system will contain a pulsar. The joint detection of a binary pulsar with LISA and SKA would not only help to constrain the parameters of the binary, but also enable investigation of other compact object physics. A pulsar(PSR)+BH can be provide stringent tests of theories of gravity, in particular the ``No-hair theorem'' \citep{Keane+2015}. Altneratively, an ultrarelativstic PSR+NS system could be used to measure the neutron star equation of state up to an order of magniute better than other proposed observations \citep{Kyutoku+2019, Thrane+2020}.

>>>>

\subsubsection{Distinguishing from WDWD population}
The population of Galactic WDWDs detectable with LISA will be several orders of magnitude larger than the more massive DCOs on which we focus in this paper \citep[e.g.][]{Korol+2017}. It is therefore imperative that we consider how to distinguish from this much more numerous population of sources.

The easiest way to check whether a source is a WDWD is to check its chirp mass. The mass of a non-rotating white dwarf cannot be larger than the Chandrasekhar limit of $1.44 \unit{M_\odot}$ \citep{Chandrasekhar+1931}, so we can take the maximum chirp mass of a WDWD to be $\sim 1.25 \unit{M_{\odot}}$. Therefore, any DCO with a chirp mass that satisfies $\mathcal{M}_c > 1.25 \unit{M_{\odot}} + 2 \Delta \mathcal{M}_c$ must not be a WDWD. We find that 17\%(23\%) of BHBHs, 20\%(24\%) of BHNSs and 2.4\%(2.5\%) of NSNSs for a 4(10)-year LISA mission satisfy this condition.

\todo{Another bit about the fact that eccentric DCOs that are resolved within the disc can be quite confidently confirmed as not WDWDs}

\subsubsection{Separating BHBHs, BHNSs and NSNSs}

\todo{}

\subsection{Matching LISA detections to pulsars with SKA}\label{sec:pulsar_matching}
Since the vast majority of the LISA detectable population of DCOs will not merge for many years, the main form of electromagnetic counterpart for the this population is pulsars. Therefore, for this section we focus only on BHNSs and NSNSs since no BHBH system will contain a pulsar. The joint detection of a binary pulsar with LISA and SKA would not only help to constrain the parameters of the binary, but also enable investigation of other compact object physics. A pulsar(PSR)+BH can be provide stringent tests of theories of gravity, in particular the ``No-hair theorem'' \citep{Keane+2015}. Altneratively, an ultrarelativstic PSR+NS system could be used to measure the neutron star equation of state up to an order of magnitude better than other proposed observations \citep{Kyutoku+2019, Thrane+2020}.

### 2021-06-15 paper/tex/sections/results.tex
progress on distinguishing

We can invert this and instead write that the chirp mass is
\begin{equation}
    \mathcal{M}_c = \frac{c^3}{G} \left( \frac{5 \pi}{48} \frac{\dot{f}_{\rm orb}}{F(e)} \right)^{3/5} \frac{1}{(2 \pi f_{\rm orb})^{11/5}},
\end{equation}
and therefore that the chirp mass uncertainty is
\begin{equation}\label{eq:chirp_mass_uncertainty}
    \frac{\Delta \mathcal{M}_c}{\mathcal{M}_c} = \frac{11}{5} \frac{\Delta f_{\rm orb}}{f_{\rm orb}} + \frac{3}{5} \frac{\Delta \dot{f}_{\rm orb}}{\dot{f}_{\rm orb}} + \frac{3}{5} \frac{\Delta F(e)}{F(e)}.
\end{equation}

@@

We use Eq.~\ref{eq:chirp_mass_uncertainty} to calculate the chirp mass uncertainty for each DCO in our sample and plot it in the lower centre panel of Fig.~\ref{fig:fiducial_pdf_distributions}. We show the distribution as a CDF that is normalised to the expected number of detections to better indicate the absolute number of detections that will have well determined chirp masses. We find that approximately 10 BHBHs and BHNSs and 5 NSNSs have measurable chirp masses (as indicated by the shaded region). We emphasise that this is a pessimistic estimate due to the pessimistic nature of how we determine the eccentricity uncertainty.

@@

\subsection{Model variations}
\todo{This will be about how the shapes change with model variations}

>>>>

We can invert this and instead write that the chirp mass is
\begin{equation}
    \mathcal{M}_c = \frac{c^3}{G} \left( \frac{5 \pi}{48} \frac{\dot{f}_{\rm orb}}{F(e)} \right)^{3/5} \frac{1}{(2 \pi f_{\rm orb})^{11/5}},
\end{equation}
and therefore that the chirp mass uncertainty is
\begin{equation}\label{eq:chirp_mass_uncertainty}
    \qty( \frac{\Delta \mathcal{M}_c}{\mathcal{M}_c} )^2 = \left( \frac{11}{5} \frac{\Delta f_{\rm orb}}{f_{\rm orb}} \right)^2 + \left( \frac{3}{5} \frac{\Delta \dot{f}_{\rm orb}}{\dot{f}_{\rm orb}} \right)^2 + \left( \frac{3}{5} \frac{\Delta F(e)}{F(e)} \right)^2.
\end{equation}

@@

We use Eq.~\ref{eq:chirp_mass_uncertainty} to calculate the chirp mass uncertainty for each DCO in our sample and plot it in the lower centre panel of Fig.~\ref{fig:fiducial_pdf_distributions}. We show the distribution as a CDF that is normalised to the expected number of detections to better indicate the absolute number of detections that will have well determined chirp masses. We find that approximately 10 BHBHs, 10 BHNSs and 5 NSNSs have measurable chirp masses (as indicated by the shaded region). We emphasise that this is a pessimistic estimate due to the pessimistic nature of how we determine the eccentricity uncertainty.

@@

\subsection{Model variations}
\todo{This will be about how the shapes of the parameter distributions change for the different model variations}
